---
title: "Using minimapR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using minimapR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
'minimapR' is a wrapper for 'Minimap2'. 'Minimap2' is a very valuable long read aligner for the Pacbio and Oxford Nanopore Technologies sequencing platforms. 'minimapR' is an R wrapper for 'minimap2' which was developed by Heng Li <me@liheng.org>. This tool aligns long reads to a reference genome and is used in many different bioinformatics workflows. 

```{r setup}
library(minimapR)
```


# Installation
'minimap2' and 'samtools' must be installed on your system along with the R packages 'Rsamtools', 'git2r', and 'pafr'. 'minimap2' can be installed on various operating systems by running the following function or following the instruction from the output of the function.
```{r installation}
minimap2_installation("/home/jake/software")
````

check if dependencies were successfully installed.
```{r check}
minimap2_check()
samtools_check()
```

# Usage
## Downloading data for example
```{r download}

```

```{r cleanup}
# Clean up
rm(list = ls())
sessionInfo()
```